\documentclass[11pt,a4paper]{article}
\usepackage[utf8]{inputenc}
\usepackage[margin=1in]{geometry}
\usepackage{xcolor}
\usepackage{titlesec}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{tcolorbox}

% --- Brand & Color Definitions ---
\definecolor{primary}{HTML}{003366}   % Dark Navy (Professional)
\definecolor{secondary}{HTML}{4682B4} % Steel Blue
\definecolor{neutral}{HTML}{333333}   % Off-black for text
\definecolor{lightbg}{HTML}{F4F6F9}   % Light grey for boxes

% --- Typography & Layout ---
\usepackage{helvet}
\renewcommand{\familydefault}{\sfdefault}
\makeatletter
\newcommand{\globalcolor}[1]{%
  \color{#1}\global\let\default@color\current@color
}
\makeatother
\AtBeginDocument{\globalcolor{neutral}}

% --- Section Styling ---
\titleformat{\section}
  {\color{primary}\normalfont\Large\bfseries}{}{0em}{}[\titlerule]
\titleformat{\subsection}
  {\color{secondary}\normalfont\large\bfseries}{}{0em}{}

\titlespacing*{\section}{0pt}{1.5ex plus 1ex minus .2ex}{1ex plus .2ex}
\titlespacing*{\subsection}{0pt}{1.2ex plus 1ex minus .2ex}{0.8ex plus .2ex}

% --- Custom Checklist Bullet (\square) ---
\newlist{checklist}{itemize}{2}
\setlist[checklist,1]{label=$\square$, leftmargin=1.5em, labelsep=0.8em, itemsep=0.4ex}
\setlist[checklist,2]{label=$\circ$, leftmargin=1.5em}

% --- Header Info Block ---
\newcommand{\resourcetitle}[3]{
    \begin{tcolorbox}[colback=primary, colframe=primary, arc=4mm, textcolor=white, center, halign=center, padding=1em]
        {\Huge \bfseries #1} \\[0.5em]
        {\large \textbf{Resource Category:} #2 \,$\cdot$\, \textbf{Updated:} #3}
    \end{tcolorbox}
    \vspace{1em}
}

\begin{document}

% =========================================================================
% RESOURCES TEMPLATE CONTENT START
% =========================================================================

\resourcetitle{GLBA Compliance Checklist}{Compliance & Security}{July 2026}

This checklist maps out the necessary regulatory actions required to adhere to the Gramm-Leach-Bliley Act (GLBA), specifically focusing on the Financial Privacy Rule and the Safeguards Rule.

\section{1. Administrative Safeguards}
Ensure the organizational protocols and personnel structures are in place.

\subsection{Program Management}
\begin{checklist}
    \item Appoint a qualified individual/Security Officer to coordinate the Information Security Program.
    \item Perform a comprehensive, documented risk assessment identifying internal and external threats to NPI (Nonpublic Personal Information).
    \item Design and implement a regular employee cybersecurity and awareness training program.
\end{checklist}

\subsection{Vendor Management}
\begin{checklist}
    \item Draft policies requiring all third-party service providers to sign GLBA-compliant data security agreements.
    \item Periodically monitor and assess the security practices of external vendors with access to systems.
\end{checklist}


\section{2. Technical & Physical Safeguards}
Deploy strong digital and physical defenses to protect consumer records.

\subsection{Access Controls \& Encryption}
\begin{checklist}
    \item Implement Multi-Factor Authentication (MFA) for all employees and users accessing customer data.
    \item Apply data encryption measures both for data at rest and data in transit.
    \item Enforce the principle of least privilege, restricting user accounts to data essential for their specific roles.
    \item Maintain secure data disposal protocols (e.g., destroying or purging records after 2 years of inactivity).
\end{checklist}

\subsection{Monitoring \& Incident Response}
\begin{checklist}
    \item Set up automated security logs and systems to actively monitor unauthorized or suspicious access attempts.
    \item Develop and regularly test a written Disaster Recovery (DR) and Business Continuity Plan (BCP).
\end{checklist}

\end{document}
